---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "forage-invertss"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Though present in the area, some key forage species - anchovy and krill - had low abundance or unusual regional abundance patterns leading to impacts to their predators.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "Krill  (<i>Euphausid spp.</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        skip    = 0,
        filter  = "species_group == \"Krill\"",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "Market Squid  (<i>Loligo opalescens</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        skip    = 0,
        filter  = "species_group == \"Market squid\"",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))",
        group_by= NULL
    ),
    error = function(e) e
)
```
Source Data: Dr. John Field (NOAA; john.field@noaa.gov) from the SWFSC
Rockfish Recruitment and Ecosystem Assessment Survey
(https://swfsc.noaa.gov/textblock.aspx?Division=FED&ParentMenuId=54&id=20615).
Additional Calculations: Samples represent catch (individuals) per standard
15 minute trawl (CPUE). Data are log(CPUE+1) transformed; Geometric means
calculated on non-zero data.
