---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "phytoplankton"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Microscopic organisms with a massive impact, phytoplankton provide nearly half of the earth's atmospheric oxygen and consume carbon dioxide on a scale equivalent to forests. At the foundation of aquatic food webs, they are critical to the health of the ocean. Toxic phytoplankton have an impact on public health and commercial fisheries.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Phytoplankton Biomass",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "year",
        col_y   = "biomass",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Pennate Diatom Abundance",
        y_label = "%",
        skip    = 0,
        filter  = NULL,
        col_t   = "year",
        col_y   = "pct_diat",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Centric Diatom Abundance",
        y_label = "%",
        skip    = 0,
        filter  = NULL,
        col_t   = "year",
        col_y   = "pct_dino",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Autotrophic Dinoflagellates Abundance",
        y_label = "%",
        skip    = 0,
        filter  = NULL,
        col_t   = "year",
        col_y   = "pct_pico",
        group_by= NULL
    ),
    error = function(e) e
)
```
<p>Some of the first principles in biological oceanography are that phytoplankton primary production supports the pelagic and benthic ecosystems and determines the rate of accumulation of organic material in the sediments. The so-called biological “pump” moves the energy harvested from sunlight by phytoplankton to the deep ocean. Phytoplankton, because they exist at the ocean-atmosphere interface, are directly affected by changes in climate.
