---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "phytoplankton"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Phytoplankton - Microscopic organisms with a massive impact, phytoplankton provide nearly half of the earth’s atmospheric oxygen and consume carbon dioxide on a scale equivalent to forests. At the foundation of aquatic food webs, they are critical to the health of the ocean. Toxic phytoplankton have an impact on public health and commercial fisheries.
<p></p>Highly anomalous ocean conditions fueled a widespread bloom of phytoplankton, including toxin-producing pennate diatoms. These toxins moved through the foodweb with various impacts, including stranded marine mammals and the longest closure of the west coast Dungeness crab fishery.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Phytoplankton Biomass",
        y_label = "(mg C/m3)",
        skip    = 0,
        filter  = "year > 1989",
        col_t   = "year",
        col_y   = "biomass",
        group_by= NULL
    ),
    error = function(e) e
)
```
 A warm water event known as the "Blob", caused a wide-spread bloom of domoic acid-producing pennate diatoms and led to the closure of the California Dungeness crab season in the Fall of 2015.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Pennate Diatom Average Per Year",
        y_label = "(mg C/m3)",
        skip    = 0,
        filter  = "yr<2017",
        col_t   = "yr",
        col_y   = "pennate",
        group_by= NULL
    ),
    error = function(e) e
)
```
Centric diatoms are often thought of as signature or "keystone" phytoplankton species within upwelling systems. Centrics were abundant from 1998-2002, but in spring 2003 became less so. Several months following the centric decrease, dinoflagellates bloomed instead and their numbers remain high. Overall phytoplankton biomass remained high, but the dominant taxa changed, and must have affected fish and other higher-trophic level organisms in as yet unexplored ways.


```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Centric Diatom Average Per Year",
        y_label = "(mg C/m3)",
        skip    = 0,
        filter  = "yr<2017",
        col_t   = "yr",
        col_y   = "centric",
        group_by= NULL
    ),
    error = function(e) e
)
```
In 2004, dinoflagellates replaced diatoms as the dominant phytoplankton taxon in Monterey Bay. This shift in "keystone" phytoplankon is associated with an increase in near surface stratification and a decrease in upwelling-favorable winds. Some species of dinoflagellates are known to produce toxic phytoplankton blooms known as "red tide".

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_dinos_mb_by_year.csv",
        title   = "Autotrophic Dinoflagellates Average Per Year",
        y_label = "(mg C/m3)",
        skip    = 0,
        filter  = "yr<2017",
        col_t   = "yr",
        col_y   = "adinos",
        group_by= NULL
    ),
    error = function(e) e
)
```
<p>Monterey Bay Aquarium Research Institute (MBARI) Biological Oceanography Group, Francisco Chavez. Epifluorescent microscopy counts; units have been converted to mg Carbon/m3. http://www.mbari.org
