---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "phytoplankton"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Microscopic organisms with a massive impact, phytoplankton provide nearly half of the earth's atmospheric oxygen and consume carbon dioxide on a scale equivalent to forests. At the foundation of aquatic food webs, they are critical to the health of the ocean. Toxic phytoplankton have an impact on public health and commercial fisheries.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/SDG14_MB_Monique.csv",
        title   = "Phytoplankton Biomass",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = "year > 1989",
        col_t   = "year",
        col_y   = "biomass",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Pennate Diatom Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "p_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Centric Diatom Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "c_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_dinos_mb_by_year.csv",
        title   = "Autotrophic Dinoflagellates Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "a_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```
<p>Monterey Bay Aquarium Research Institute (MBARI) Biological Oceanography Group, Francisco Chavez. Epifluorescent microscopy counts; units have been converted to mg Carbon/m3. http://www.mbari.org
