---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "phytoplankton"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Phytoplankton, microscopic in size with a massive impact. They provide nearly half of the earth's atmospheric oxygen and consume carbon dioxide on a scale equivalent to forests. At the foundation of aquatic food webs, they are critical to the health of the ocean. Toxic phytoplankton have an impact on public health and commercial fisheries.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_biomass_mb_by_year.csv",
        title   = "Phytoplankton Biomass",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "b_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```
 A warm water event known as the "Blob", caused a wide-spread bloom of domoic acid-producing pennate diatoms and led to the closure of the California Dungeness crab season in the Fall of 2015.

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Pennate Diatom Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "p_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```
Centric diatoms are often thought of as signature or "keystone" phytoplankton species within upwelling systems. Centrics were abundant from 1998-2002, but in spring 2003 became less so. Several months following the centric decrease, dinoflagellates bloomed instead and their numbers remain high. Overall phytoplankton biomass remained high, but the dominant taxa changed, and must have affected fish and other higher-trophic level organisms in as yet unexplored ways.


```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_diatoms_mb_by_year.csv",
        title   = "Centric Diatom Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "c_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```
In 2003, dinoflagellates replaced diatoms as the dominant phytoplankton taxon in Monterey Bay. This shift in "keystone" phytoplankon is associated with an increase in near surface stratification and a decrease in upwelling-favorable winds. Some species of dinoflagellates are known to produce toxic phytoplankton blooms known as "red tide".

```{r}
tryCatch(
    plot_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/phytoplankton/efm_dinos_mb_by_year.csv",
        title   = "Autotrophic Dinoflagellates Abundance",
        y_label = "mg C m-3",
        skip    = 0,
        filter  = NULL,
        col_t   = "yr",
        col_y   = "a_abun",
        group_by= NULL
    ),
    error = function(e) e
)
```
Some of the first principles in biological oceanography are that phytoplankton primary production supports the pelagic and benthic ecosystems and determines the rate of accumulation of organic material in the sediments. The so-called biological “pump” moves the energy harvested from sunlight by phytoplankton to the deep ocean. Phytoplankton, because they exist at the ocean-atmosphere interface, are directly affected by changes in climate.
